---
title: "Stat133-workout1"
author: "Dui"
date: "2018-10-03"
output: md_document
---

## Ranking of Teams

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = 'workout01-Dui-Lee_files/')
```

```{r}
library(readr)
library(dplyr)
library(ggplot2)

nbateams = read_csv('../data/nba2018-teams.csv')
```

### Basic Rankings

#### ranking the teams according to salary, arranged in decreasing order. Vertical line indicates the average salary. 

```{r rank_by_total_salary}
nbateams <- arrange(nbateams, desc(salary))
ggplot(nbateams, aes(x = reorder(team, salary), y = salary)) + geom_bar(stat='identity') + coord_flip() +
  geom_hline(yintercept = mean(nbateams$salary), color = 'red') +
  labs(title = 'NBA Teams ranked by Total Salary', x = 'Team', y = 'Salary(in millions)')
  
```

#### Create another bar chart of teams ranked by total points. Vertical line indicating the average team points. 

```{r rank_by_total_points}
ggplot(nbateams, aes(x = reorder(team, points), y = points)) + geom_bar(stat='identity') + coord_flip() +
  geom_hline(yintercept = mean(nbateams$points), color = 'red') +
  labs(title = 'NBA Teams ranked by Total Points', x = 'Team', y = 'Points')
```

#### Use efficiency to obtain a ranking, and create an associated bar chart of teams ranked by total efficiency. Vertical line indicates the average team efficiency.

```{r rank_by_total_efficiency}
ggplot(nbateams, aes(x = reorder(team, efficiency), y = efficiency)) + geom_bar(stat='identity') + coord_flip() +
  geom_hline(yintercept = mean(nbateams$efficiency), color = 'red') +
  labs(title = 'NBA Teams ranked by Total efficiency', x = 'Team', y = 'Efficiency')
```

#### Create a fourth bar chart but this time using your own index. 

* I have used the index 'efficiency / experience'. One of the criteria of ranking team can be looking at how much total efficiency of the players that each team is getting with respect to player's total experience. With a same amount of experience, the team with higher efficiency can be treated as a better team. Hence, we can compare the ratio of efficiency and experience by dividing efficiency with experience, and get the comparison over different teams. 

* Graph follows as below

```{r rank_by_total_eff_per_ex}
new_index <- nbateams %>% mutate(eff_per_ex = efficiency / experience)
ggplot(new_index, aes(x = reorder(team, eff_per_ex), y = eff_per_ex)) + geom_bar(stat='identity') + coord_flip() +
  geom_hline(yintercept = mean(new_index$eff_per_ex), color = 'red') +
  labs(title = 'NBA Teams ranked by Total Efficiency Divided by Total Experience', x = 'Team', y = 'Efficiency / Experience')
```

## Comments and Reflections
* It was my first time working on a project with such file structure. I do feel that it is an organized to way work through a project, and will be definitely useful in the future. Yet the practice do require time and effort.
* It was not my first time using relative paths, but it was good refresher
* It was my first time using an R script. I was lagging a little bit as I was commenting and typing in codes with out inserting R chunk. But I got used to it.
* I think ggplot was quite hard as it used more layers like adding vertical line and ordering the y axis. 
* Working with dplyr was on the easier side as it is quite logical to follow
* I consulted a lot of Piazza, class material and google search
* It took be 6~7 hours, with setting data dictionary and ggplot taking the most amount of time.
* manipulating the data into the way I want to present is definitely interesting. 
