---
title: "Lab03-Dui-Lee"
author: "Dui"
date: "2018³â 9¿ù 12ÀÏ"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r eval=FALSE}
#Look at the man documentation of ls to find out how to list the contents in reverse order
ls -r

#How would you list the contents in long format arranged by time?
ls -l -t

#Find out how to use the wildcard * to move list all the files with extension .txt
ls -F *txt

#Use the wildcard * to move list all the files with extension .csv in reverse order
ls -F *csv -r

#Find out how to use the wilcard ? to list .csv files with names made of 4 characters
ls ????.csv

#Adapt the command to list .csv files with names containing the number 2.
ls *[2]*.csv

#Find out how to list files with names containing any number.
ls *[0-9]*
  
#Use the command mv to move the bread.txt file to the folder txt-files
mv bread.txt data/txt-files

#Use the wildcard * to move all the text files to the directory txt-files
mv *.txt data/txt-files

#Use the wildcard * to move all the .csv files to the directory csv-files
mv *.csv data/csv-files

#Use the command cp to copy the bread.txt file (the one inside the folder txt-files) to the copies directory
cp data/txt-files/bread.txt copies

#Use the wildcard * to copy all the .txt files in the directory copies
cp data/txt-files/*.txt copies

#Use the wildcard * to copy all the .csv files in the directory copies
cp data/csv-files/*.csv copies

#Use the command mv to rename the file bread.txt as bread-recipe.txt
mv bread.txt bread-recipe.txt

#Rename the file Fisher.csv as iris.csv
mv Fisher.csv iris.csv

#Rename the file btaco.txt as breakfast-taco.txt
mv btaco.txt breakfast-taco.txt

#Rename the directory copies as copy-files
mv copies copy-files

#Find out how to use the rm command to delete the .csv files that are in copy-files
rm /copy-files/*.csv

#Find out how to use the rm command to delete the directory copy-files
rm -rf copy-files

#List the contents of the directory txt-files displaying the results in reverse (alphabetical) order
ls data/txt-files -r
```

##Abalone Dataset

* What¡¯s the character delimiter?
    + the character delimiter is comma
* Is there a row for column names?
    + no row for a column names
* Are there any missing values? If so, how are they codified?
    + no missing values
* What is the data type of each column?
    + Name | Data Type 
------|-------
sex | nominal
length | continous
diameter | continous
height | continous
whole height | continous
shucked height | continous
viscera height | continous
shell height | continous
rings | integer

##Some Bash Commands
```{r eval=FALSE}
#Use the file command to know what type of file is abalone.data.
##abalone.data: ASCII text, with CRLF line terminators

#Use the word count command wc to obtain information about: 1) newline count, 2) word count, and 3) byte count, of the abalone.data file.
##4177   4177 196050 abalone.data

#See the man documentation of wc and learn what option you should use to otabin only the number of lines in abalone.data.
wc abalone.data -l

#See the man documentation of head and learn what option you should use to display only the first 5 files in abalone.data.
head abalone.data -n 5

#See the man documentation of tail and learn what option you should use to display only the last 3 files in abalone.data.
tail abalone.data -n 3
```

##Basic Importing

```{r}
abalone <- read.table("abalone.data", sep = ",")
head(abalone)

tail(abalone)

str(abalone, vec.len = 1)
```

```{r}
# Create a vector column_names for names of each column. Use the names displayed in the section ¡°7. Attributes Information¡±
column_names <- c("Sex", "Length", "Diameter", "Height", "Whole weight", "Shucked weight", "Viscera weight", "Shell weight", "Rings")
# Create another vector column_types with R data types
column_types <- c("character", "real", "real", "real", "real", "real", "real", "real", "integer" )
```

```{r}
# Look at the documentation of the function read.table() and try to read the abalone.data table in R
abalone <- read.table("abalone.data", sep=',', col.names=column_names, colClasses = column_types)

str(abalone)
```

```{r}
# Now re-read abalone.data with the read.csv() function. Name this data as abalone2
abalone2 <- read.csv("abalone.data")
str(abalone2)
```

```{r}
# How would you read just the first 10 lines in abalone.data?
abalone10 <- head(read.table("abalone.data"), n = 10L)
abalone10
```

```{r}
# How would you skip the first 10 lines in abalone.data, in order to read the next 10 lines (lines 11-20)?
abalone20 <- tail(head(read.table("abalone.data"), n = 20L), n = 10L)
abalone20
```

```{r}
# Use R functions to compute descriptive statistics,
summary(abalone)
```