---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

## Overview

The package '"roller"' is package for simulating rolling a device a given number of times.
One can create own device with customized sides and probability, and can simulate rolling
for desired number of times. Visualization of rolls is also available. 

* 'device()' creates a device to roll (of class 'device')
* 'roll()' roll the device object, produces class of 'roll'
* 'plot()' plot method for 'roll' objects to draw barchart of roll results
* 'summary()' method for 'roll' object

## Motivation

This package is for simulating rolling a customized device

## Installation

```r
# development version from GitHub:
#install.packages("devtools") 
# install "roller" (without vignettes)
devtools::install_github("hw-stat133-duilee/roller")
# install "roller" (with vignettes)
devtools::install_github("hw-stat133-duilee/roller", build_vignettes = TRUE)
```


## Usage

```{r}
library(roller)

# default device
device1 <- device()
device1

# roll the device(default time = 1)
roll20 <- roll(device1, 20)
roll20

#summary
summary(roll20)

#add ten more toss
roll20 + 10

#plot rolls
plot(roll20)
```
