---
title: "Introduction to Roller"
author: "Dui Lee"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to roller}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(roller)
```

## Rolling a device

The package '"roller"' is package for simulating rolling a device a given number of times.
One can create own device with customized sides and probability, and can simulate rolling
for desired number of times. Visualization of rolls is also available. 

## Creating a device

To create a device, use the function 'coin()'

```{r}
demodev <- device()
demodev
```

By default, device will create a device with side 1 and 2 and with 0.5 probability for each. 
To create your own device, you need to specify the sides and probabilties with following,
- sides has at least 2 elemens
- sides has no duplicate
- probabilities all have value between 0 and 1
- probabilities add up to one

## Rolling the device

To roll your device, use 'roll()', with your designated device in the input. 

```{r}
roll(demodev)
```
By default, 'roll()' will your roll your device once and return the result.
You can specify the number of times you want to roll your device,
by specifying 'times'

```{r}
demoroll <- roll(demodev, times = 10)
demoroll
```

You can also explore related information of your roll result.

- use 'rolls' to extract the rolls result only
```{r}
demoroll$rolls
```

- use 'sides' to examine the sides of given device
```{r}
demoroll$sides
```

- use 'prob' to examine the probability of each side
```{r}
demoroll$prob
```

- use 'total' to figure out total number of rolls
```{r}
demoroll$total
```

## Summary Method for object 'rolls'

- Summary method can be used by 'summary()' with rolls object as input
```{r}
summary(demoroll)
```
Symmary will provide a datafram containing 3 columns of 'side', 'count' and 'prop'. 
- side : the sides of the rolled device
- count : the frequency(count) of each side of the rolled device
- prop : the relative frequency(proportion) of each side of the rolled device

The dataframe can be accessed by using 'freqs'
```{r}
demosummary <- summary(demoroll)
demosummary$freqs
```


## Plot Method for object 'rolls'

The plot method for object 'rolls' can be used with function 'plot()' with 'rolls' object as input

```{r}
plot(demoroll)
```

'plot()' will return a barchart of proportions

## Addtional Methods

- An extraction method to extract the value of a given roll, following regular r indexing
```{r}
demoroll[2]
```

- A replacement method to replace the value of a given roll also follows regular r indexing
```{r}
demoroll[2] <- 1
demoroll[2]
```

- an addition method will add more roll, i.e to add 10 more rolls,
```{r}
demoroll + 10
```


