---
title: "Lab02"
author: "Dui Lee"
date: "2018³â 9¿ù 5ÀÏ"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
rdata <- "https://github.com/ucb-stat133/stat133-fall-2018/raw/master/data/nba2018-salary-points.RData"
download.file(url = rdata, destfile = 'nba2018-salary-points.RData')
data <- load('nba2018-salary-points.RData')
```


## Vector and other data structures

```{r}
length(age)
head(age)
tail(age)
summary(age)
house['Bedrooms']

```

```{r}
length(experience)
head(experience)
tail(experience)
summary(experience)
```


```{r}
length(player)
head(player)
tail(player)
summary(player)
```

* all chosen objects have same length

```{r}
sum(is.na(age))
sum(is.na(experience))
sum(is.na(player))
```
* No objects contain missing value
```{r}
class(age)
class(experience)
class(player)
```
 * classes of age, experience and player are integer, character and character
 * You can use str or class to find out if the object is a vector
 * You can use mode to find out the data type of the object
 
##Manipulating vectors
 
```{r}
four <- head(player, n = 4)
four
# four[1] returns first player
four[1]
# four[0] doesn't return a player name as index is wrong
four[0]
# four[-1] returns everything except for item 1
four[-1]
# four[-c(1,2,3)] returns everything except for item 1,2,3 
four[-c(1,2,3)]
# four[5] returns no value since no item at index 5
four[5]
# four[c(1,2,2,3,3,3)] returns value of following index
four[c(1,2,2,3,3,3)]
```
 
```{r, eval=FALSE}
#all the even elements in player
player[seq.int(2, length(player), 2)]
#all the odd elements in salary
salary[seq.int(1, length(salary), 2)]
#all multiples of 5 (e.g. 5, 10, 15, etc) of team
team[seq.int(5, length(team), 5)]
#elements in positions 10, 20, 30, 40, etc of scored
scored[seq.int(10, length(scored), 10)]
#all the even elements in team but this time in reverse order
team[seq.int(length(team), 1, -1)]
```

##Logical Subsetting

```{r}
# AND
TRUE & TRUE
TRUE & FALSE
FALSE & FALSE

# OR
TRUE | TRUE
TRUE | FALSE
FALSE | FALSE

# NOT
!TRUE
!FALSE
```

```{r}
#players in position Center, of Warriors (GSW)
player[team == 'GSW' & position == 'C']
#players of both GSW (warriors) and LAL (lakers)
player[team == 'GSW' & team == 'LAL']
#players in positions Shooting Guard and Point Guards, of Lakers (LAL)
player[(position == 'SG' | position == 'PG') & team == 'LAL' ]
#subset Small Forwards of GSW and LAL
sf <- player[position == 'SF' & (team == 'GSW' | team == 'LAL')]
sf
#name of the player with largest salary
player[salary == max(salary)]
#name of the player with smallest salary
player[salary == min(salary)]
```
```{r}
#name of the player with largest number of scored points
total <- points1 + points2*2 + points3*3
names(total) <- player
player[total == max(total)]
#salary of the player with largest number of points
salary[player == player[total == max(total)]]
```
```{r}
#largest salary of all Centers
max(salary[position == 'C'])
#team of the player with the largest number of scored points
team[player == player[total == max(total)]]
#name of the player with the largest number of 3-pointers
player[ points3 == max(points3)]
```
```{r}
player[scored == max(scored)]
```

##Subsetting with Character Vectors
```{r}
names(player)
warriors_player <- player[team == 'GSW']
warriors_salary <- salary[team == 'GSW']
warriors_points <- scored[team == 'GSW']
names(warriors_salary) = warriors_player

warriors_salary["Andre Iguodala"]

warriors_salary[c("Stephen Curry", "Kevin Durant")]

```

##Some plotting

```{r}
plot(warriors_points, warriors_salary)
text(warriors_points, warriors_salary, labels = warriors_player)
```

```{r}
log_scored <- log(warriors_points)
log_salary <- log(warriors_salary)

plot(log_scored, log_salary)
text(log_scored, log_salary, labels = warriors_player)
```

## Recycling

```{r}
#the salaries in millions of dollars
salary_millions = salary / 1000000
#Take the values in points1, points2, and points3 and figure out to create a new vector scored_points that gives you the same values of points
scored_points = points1 + points2*2 + points3*3
```


##Manipulating Factors

```{r}
#positions of Warriors
position_fac <- factor(position[team == 'GSW'])
table(position_fac)
```

```{r}
#positions of players with salaries > 15 millions
factor(position[salary > 15000000])
#frequencies (counts) of positions with salaries > 15 millions
table(factor(position[salary > 15000000]))
```
```{r}
#relative frequencies (proportions) of ¡®SG¡¯ (Shooting Guards) in each team
prop.table(table(factor(team[position == 'SG'])))
```

##More Plots
```{r}
plot(scored, salary, col=position_fac, pch = 0:5, cex = 1.5, xlab='Player Salary', ylab='Points Scored')
```


