---
title: "Lab12-Dui-Lee"
author: "Dui"
date: "2018³â 11¿ù 14ÀÏ"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(XML)
library(xml2)
library(rvest)
library(magrittr)
```

```{r}
# Assemble url (so it fits on screen)
basket <- "https://www.basketball-reference.com"
gsw <- "/teams/GSW/2017.html"
gsw_url <- paste0(basket, gsw)

# download HTML file to your working directory
download.file(gsw_url, 'gsw-roster-2017.html')

# Read GSW Roster html table
gsw_roster <- readHTMLTable('gsw-roster-2017.html')
```

```{r}
gsw_roster
```

```{r}
# Assemble url (so it fits on screen)
basket <- "https://www.basketball-reference.com"
bos <- "/teams/BOS/2017.html"
bos_url <- paste0(basket, bos)

# download HTML file to your working directory
download.file(bos_url, 'bos-roster-2017.html')

# Read BOS Roster html table
bos_roster <- readHTMLTable('bos-roster-2017.html')

bos_roster
```

##2016-17 NBA Season Summary

```{r}
nba_html <- paste0(basket, "/leagues/NBA_2017.html")

xml_doc <- read_html(nba_html)

xml_doc
```

```{r}
xml_text <- xml_doc %>% html_text()

```

```{r}
# content of h2 nodes
xml_doc %>%
  html_nodes("h2") %>%
  html_text() 
```

###Use html_nodes() and html_text() to extract the values of nodes:

- "h1"
- "strong"
- "button"

```{r}
xml_doc %>%
  html_nodes("h1") %>%
  html_text()
```

```{r}
xml_doc %>%
  html_nodes("strong") %>%
  html_text()
```

```{r}
xml_doc %>%
  html_nodes("button") %>%
  html_text()
```

```{r}
# node with an attribute
xml_doc %>%
  html_nodes("p.listhead") %>%
  html_text()
```

##Extracting href attributes

```{r}
# extracting first table 
xml_table1 <- xml_doc %>%
  html_nodes("table") %>%
  extract(1)

class(xml_table1)
```
```{r}
xml_tables <- xml_doc %>%
  html_nodes("table") %>%
  extract(1:2)

xml_tables %>% 
  html_nodes("a") %>%
  html_attr("href")
```

###Your Turn

- Store the href attributes in a character vector hrefs.
- Use string manipulation functions to create a character vector teams that contains just the team abbreviations: e.g. "BOS", "CLE", "TOR", ...
- Create a character vector files with elements: "BOS-roster-2017.csv", "CLE-roster-2017.csv", "TOR-roster-2017.csv", ...
- Use the object basket and the first element of hrefs (i.e. hrefs[1]) to assemble a team_url like the one used for gsw_url:

```{r}
library(stringr)

hrefs <- xml_tables %>% 
  html_nodes("a") %>%
  html_attr("href")

teams <- str_sub(hrefs, 8, 10)

files <- paste0(teams, "-roster-2017.csv")

team_url <- paste0(basket, hrefs[1])
```

- Read the html document of team_url.
- Use html_table() to extract the content of the html table as a data frame called roster.

```{r}
xml_doc2 <- read_html(team_url)


xml_table <- xml_doc2 %>%
  html_nodes("table") %>%
  extract(1)

roster <- html_table(xml_table)[[1]]

roster
```
- Store the data frame in a csv file: "BOS-roster-2017.csv".
```{r}
write.csv(roster, files[1])
```

- Create a for () loop to extract a handful of the roster tables as data frames.
Store each table in its own csv file: e.g. "GSW-roster-2017.csv"
```{r}
for (i in 1:5) {
  team_url <- paste0(basket, hrefs[i])
  xml_doc2 <- read_html(team_url)
  xml_table <- xml_doc2 %>%
    html_nodes("table") %>%
    extract(1)
  roster <- html_table(xml_table)[[1]]
  write.csv(roster, files[i])

}
```

