---
title: "Warmup03-Dui-Lee"
author: "Dui"
date: "2018³â 9¿ù 16ÀÏ"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Reading the Data Into R
* the data has a header containing the variable names
* looks like the values are seperated by a tab

```{r}
github <- 'https://github.com/ucb-stat133/stat133-fall-2018/' 
repo <- 'raw/master/data/saratoga.txt' 
house <- read.table(paste0(github, repo), sep = "\t", header = TRUE)
```

```{r}
#structure of the data
str(house)
```

##Examine Price
```{r}
#summary and histogram of price
summary(house$Price)
hist(house$Price)
```
```{r}
# log transformation looks more symmetric.
log_price <- log(house$Price)
hist(log_price)
```

```{r}
#Five houses are what we call cheap
cheap <- log_price < 10.5
sum(cheap)
```
```{r}
# cheap house values
house$Price[cheap]
```
```{r}
# new house data without rows that contain cheap houses
rows = cheap
house = house[!rows,]
```

## Explore Living Area
```{r}
#Summary of the living area
summary(house$Living.Area)
```
```{r}
#Histogram of the living area
hist(house$Living.Area)
```
```{r}
#Logarithmic histrogram
values = log(house$Living.Area)
hist(values)
```

```{r}
# 6.8 in logarithms value cooresponds to roughly 900 in original units of measurement
exp(6.8)
```

##Transforming Variables into Factors

```{r}
#Transform bedroom vector to more factor-friendly environment
BR = house$Bedrooms
BR[BR > 5] <- 5
BR[BR < 2] <- 2
```

```{r}
# After factoring Bedrooms, the summary no longer shows the descriptive statistics but it now shows the frequency for each level. 
BR= factor(BR, labels = c("2- BR", "3 BR", "4 BR", "5+ BR"))
summary(BR)
```

##Plotting Price against Living Area

```{r}
#color vectors
my_colors = c("aquamarine3", "darkgoldenrod2", "coral2", "mediumorchid3")
br_colors = my_colors[c(1:4)]
```
```{r}
plot( Price ~ Living.Area, data = house, log = "xy", main = "", xlab = "Living Area (log sq ft)", ylab = "Price (log $)", col = br_colors, pch = 19, cex = 0.4)
legend("bottomright", fill = my_colors, legend = levels(BR), title = "# Bedrooms", cex = 0.75)
```

##Number of Fireplaces
```{r}
FP = house$Fireplaces
FP[FP > 1] = 1
FP = factor(FP, labels = c("None", "At least 1"))
```

```{r}
#Price per square foot of the house
Psq = house$Price / house$Living.Area
fp_colors = my_colors[c(1,2)]
```

```{r}
#Plot price per square foot against price
plot( Psq ~ Price, data = house, log = "xy", main = "", xlab = "Price (log $)", ylab = "Price per Sq foot (log sq foot)", col = fp_colors, pch = 19, cex = 0.4)
legend("bottomright", fill = my_colors, legend = levels(FP), title = "Fireplaces", cex = 0.75)
```

* As seen from the scatter plot, having fireplaces does not particularly make the house more expensive.
* the relationship between price and price per square foot is positive linear relationship. As price increase, price per square foot increase.
* One explanation for this result could be that when house is larger there tend to be more optional things built in the house such as swimming pool, garden, playground and etc. Hence it costs extra money than just building the house. So the price per square feet also increase. 