---
title: "warmup07-Dui-Lee"
author: "Dui"
date: "2018³â 11¿ù 10ÀÏ"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
#import the data
library("readr")
data = read_csv("text-emotion.csv")

```

##1) Number of characters per tweet

- Count the number of characters in the tweet contents; create a vector for this purpose.
```{r}
tweetlen <- nchar(data$content)
```

- Display the summary() of the vector obtained above
```{r}
summary(tweetlen)
```

- Likewise, graph a histogram of these counts. To plot the histogram, use a bin width of 5 units: 1-5, 6-10, 11-15, 16-20, etc. In other words: the first bin involves tweets between 1 and 5 characters (inclusive), the second bin involves tweets containing between 6 and 10 characters (inclusive), and so on.
```{r}
hist(tweetlen,breaks = c(5*0:34), las =1,xlab = '# of characters' ,main ="Histogram of tweet lengths")
```

- Are there any tweets with 0 characters?
```{r}
#No tweets with 0 characters
sum(tweetlen == 0)
```

- Are there any tweets with 1 character? 
```{r}
# 4 tweets with length 1
sum(tweetlen == 1)

#contents of length 1 tweets
data$content[tweetlen == 1]

#positions of length 1 tweets
which(tweetlen == 1)
```

- What is the tweet with the most characters (i.e. max length)?
```{r}
#number of charcters for max length tweet
max(tweetlen)

#its content
data$content[which(tweetlen == max(tweetlen))]

#its location
which(tweetlen == max(tweetlen))
```

##2) Sentiment

- What are the different types of sentiments (i.e. categories)?

```{r}
levels(factor(data$sentiment))
```
- Compute the frequencies (i.e. counts) of each sentiment

```{r}
table(factor(data$sentiment))
```

- Graph the relative frequencies (i.e. proportions) with a horizontal barplot (bars horizontally oriented) in decreasing order, including names of sentiment types.

```{r}
library(ggplot2)
tbl = table(factor(data$sentiment)) / 40000
names(tbl)


df = data.frame("sentiment" = sort(tbl))
df

ggplot(df, aes(x = sentiment.Var1, y = sentiment.Freq)) + geom_bar(stat='identity') + coord_flip() +
  labs(title = 'Sentiment Frequency', x = 'Frequency', y = 'Sentiment')
```

- Sentiment and length of tweets: compute a table with the average length of characters per sentiment (i.e. average number of characters for neutral tweets, for happy tweets, etc.). Display this table.
```{r}
library(dplyr)

avgtbl <- data %>% mutate('leng' = tweetlen) %>% select(sentiment, leng) %>% group_by(sentiment) %>% summarise(avg = mean(leng))

avgtbl
```

##3) Author (usernames)

Confirm that the values in column author follow each of the rules for valid usernames:
- No longer than 15 characters (if you find usernames longer than 15 characters, display them)

```{r}
#no username longer than 15
userlen <- nchar(data$author)
sum(userlen > 15)
```

- Contain alphanumeric characters and underscores (if you find usernames containing other symbols, display them)
```{r}
library(stringr)

alphanum <- function(x) {
  chklist <- str_split("abcdefghijklmnopqrstuvwxyz0123456789_", '')
  y = tolower(x)
  
  for (i in (1:nchar(x))) {
    if (sum((substr(y, i, i) == chklist[[1]])) == 0) {
      return(FALSE)
    }
  }
  return(TRUE)
}

chk <- rep(0, 40000)
for (i in (1:40000)) {
  chk[i] = alphanum(data$author[i])
}

sum(chk)

#there is one username with dash, not underscore
data$author[!chk]
```

- What is the number of characters of the shortest usernames? And what are the names of these authors? (write commands to answer these questions)
```{r}
#shortest username has length 2
min(userlen)
#names of shortest username
data$author[which(userlen == min(userlen))]
```

##4) Various Symbols and Strings

- How many tweets contain at least one caret symbol "??" 

```{r}
#40 tweets with at least one caret symbol
sum(str_detect(data$content,'\\Q^\\E'))

```

- How many tweets contain three or more consecutive dollar symbols "$" 
```{r}
#7 tweets with three or more consecutive dollar symbols
sum(grepl("\\Q$$$\\E", data$content))

```

- How many tweets do NOT contain the characters "a" or "A"
```{r}
#1875 tweets do not contain the characters "a" or "A"
sum(!(grepl("a|A", data$content)))

```

- Display the first 10 elements of the tweets that do NOT contain the characters "a" or "A"
```{r}
head(data$content[!(grepl("a|A", data$content))], 10)
```

-  Number of exclamation symbols "!": compute a vector with the number of exclamation symbols in each tweet, and display its summary().

```{r}
exclamnum <- str_count(data$content, '!')
summary(exclamnum)

```

- What¡¯s the tweet (content) with the largest number of exclamation symbols !? Display its content. 
```{r}
data$content[which(exclamnum == max(exclamnum))]
```

- How many tweets contain the individual strings "omg" or "OMG" (write a command to answer this question). For example:
```{r}
#138 tweets with the individual strings "omg" or "OMG"
sum(grepl("^omg | omg | omg$|^OMG | OMG | OMG$", data$content))
```

##5) Table of Average Number of Patterns by Sentiment

- Write code to create (and display) a table (e.g. data frame, tibble, matrix) in which the rows correspond to the unique types of sentiments, and the columns correspond to: 
1. average number of lower case letters 
2. average number of upper case letters 
3. average number of digits 
4. average number of punctuation symbols 
5. average number of spaces 

```{r}
avgtbl2 <- data %>% mutate('lowernum' = str_count(content, "[[:lower:]]"),
                'uppernum' = str_count(content, "[[:upper:]]"),
                'digitnum' = str_count(content, "[[:digit:]]"),
                'puncnum' = str_count(content, "[[:punct:]]"),
                'spacenum' = str_count(content, "[[:space:]]")) %>%
  select(sentiment, lowernum, uppernum, digitnum, puncnum, spacenum) %>% 
  group_by(sentiment) %>% 
  summarise_all(mean) %>% 
  rename("Avg # of lower case letters" = lowernum,
         "Avg # of uppter case letters" = uppernum,
         "Avg # of digits" = digitnum,
         "Avg # of punctuations" = puncnum,
         "Avg # of spaces" = spacenum)

avgtbl2
```

